EvoSwarm: A Cloud-Native Architecture for the Reproducible Execution of Multi-population Optimization Algorithms

### 2020-05-15 draft.tex
Explanationa added.
If I add more text the figure moves to the last page. I had to remove some words in order to make the text fit,

  \includegraphics[width=0.30\textwidth]{GAOnly_f005}&
  \includegraphics[width=0.30\textwidth]{PSOOnly_f005}&
  \includegraphics[width=0.30\textwidth]{GAPSO_f005}\\
  \end{tabular}
  \vspace{-3ex}
   \caption{
Scaling of expected runtime (RT defined as the number of function
evaluations to reach a target function value for the first time) for  
each problem dimension. Target values $\Delta f$ = 10, 1, $10^{-1}$, $10^{-2}$,$10^{-3}$,$10^{-5}$,$10^{-8}$
(the exponent and line colors are given in the legend of $f_1$ in the top row). 
Lines are the average RT (aRT); Cross ($+$): median RT of successful runs to reach
the most difficult target that was reached at least once (but not always);
Cross (\textcolor{red}{$\times$}): maximum number of f-evaluations in any trial. 
All values are divided by dimension and plotted as $log_{10}$ values versus dimension.
% More explanation for those not familiar with BBOB - JJ
% I think is more clear? - M
% Almost everything, but the cream-colored rhombs in the bottom...
}
\label{fig:bbob}
\end{figure*}

>>>>

  \includegraphics[width=0.30\textwidth]{GAOnly_f005}&
  \includegraphics[width=0.30\textwidth]{PSOOnly_f005}&
  \includegraphics[width=0.30\textwidth]{GAPSO_f005}\\
  \end{tabular}
  \vspace{-3ex}
   \caption{
Scaling of expected runtime (RT defined as the number of function 
evaluations \#FE) to reach a target for  
each dimension. Target values $\Delta f$ = 10, 1, $10^{-1}$, $10^{-2}$,$10^{-3}$,$10^{-5}$,$10^{-8}$
(the exponent and colors are given in the legend of $f_1$). 
Lines are the average RT; Cross ($+$): median RT of successful runs to reach
the most difficult target that was reached at least once;
Cross (\textcolor{red}{$\times$}): maximum \#FE in any trial. 
Values are divided by dimension and plotted as $log_{10}$.
The light thick line with diamonds indicates the theoretical best algorithm from BBOB 2009 for the 
most difficult target.
% More explanation for those not familiar with BBOB - JJ
% I think is more clear? - M
% Almost everything, but the cream-colored rhombs in the bottom...
}
\label{fig:bbob}
\end{figure*}
